---
title: 'null'
output:
  html_document: default
  pdf_document: default
  word_document: default
---
```{r setup}
knitr::opts_knit$set(root.dir = './output')

```

```{r Initial formatting, include=FALSE}
knitr::opts_chunk$set(echo=FALSE)


load("../summary_mod.RData")


summary$ID_time <- as.numeric(summary$ID_time)
summary$run <-as.factor(summary$run)
summary$tunnel <-as.factor(summary$tunnel)
summary$ID <- as.factor(summary$ID)
summary$FR <- summary$front_true/(summary$front_false+summary$front_true)
summary$ID_press <- paste(summary$ID, summary$npress, sep ="_")
lme.final <- lme.plot

library(nlme)
library(MuMIn)
library(tidyverse)
library(flextable)
library(ggplot2)
library(ggh4x)
devtools::install_github("thomasp85/scico")
library(scico)

#create idealized dataframe with fixed speed for plotting
ideal <- expand.grid(ID=unique(summary$ID),
                     temp_mean=c(12:21),
                     press_mean = c(1:8),
                     speedBL = c(0.6)
                  
)

ideal <- ideal %>% 
  left_join(summary %>% select(ID, startmass, run, tunnel), by = "ID")

ideal <- ideal %>%  distinct(.keep_all = T)

ideal$resp <- exp(predict(lme.plot, newdata = ideal, group = ID))
ideal$resp_glob <- exp(predict(lme.plot, newdata = ideal, level = "0"))
ideal_1 <- ideal %>% filter(press_mean == 1)


```

## Tables for manuscript

**Tab 1** Summary of biological and experimental paramaters for individual eels

```{r Tab 1}


biomasses$ID <- biomasses$ID %>% str_replace_all(c("a" = "A", "b" = "B", "c" = "C", "d" = "D", "e" = "E", "f" = "F", "g" = "G", "h" = "H", "i" = "I"))

align(flextable(biomasses %>%
            left_join((swimtime %>% select(ID, time_d, distance)), by = c("ID_old" = "ID")) %>%
            select("ID", "Length (cm)", "Silvering Index*", "Biomass at start (g)", "Biomass at end (g)", "Fat at start (% WM)", "Fat at end (% WM)", "Silvering Index*", "time_d", "distance") %>%
            mutate(time_d = round(time_d, 1),
                   distance = round(distance, 0)) %>% 
            rename("Swim time (d)" = time_d,
                   "Swimming distance (km)" = distance)) %>% 
  colformat_num(big.mark   = "") %>%
  autofit(add_w = -0.5), align = "center", part = "all")
```

\*according to Durif et al. (2005)\
\
\
\

**Tab 2** Mean and range of observed temperatures and velocities (at the respective presets) and resulting oxygen consumption rates (mg/kg * h^-1), calculated as the arithmetic mean (and range) of the mean per individual (for individual values see Tab S1). Observed pressure not shown since deviations from the nominal pressure were negligibly small 

```{r Tab 3}

summ_by_ID <- summary %>% 
            group_by(ID, ntemp, npress) %>% 
                       summarize(mean_resp = mean(resp),
                                 min_resp = min(resp),
                                 max_resp = max(resp),
                                 sd_resp = sd(resp),
                                 mean_temp = mean(temp_mean),
                                 min_temp = min(temp_mean),
                                 max_temp = max(temp_mean),
                                 sd_temp = sd(temp_mean),
                                 mean_speed = mean(speedBL),
                                 min_speed = min(speedBL),
                                 max_speed = max(speedBL),
                                 sd_speed = sd(speedBL)
                                 ) 
  

flextable(summ_by_ID %>%
            group_by(ntemp, npress) %>% 
            summarise(resp_mean = round(mean(mean_resp), 1),
                      resp_sd = round(sd(mean_resp), 1),
                      resp_min = round(min(mean_resp), 1),
                      resp_max = round(max(mean_resp), 1),
                      temp_mean = round(mean(mean_temp), 1),
                      temp_sd = round(sd(mean_temp), 1),
                      temp_min = round(min(mean_temp), 1),
                      temp_max = round(max(mean_temp), 1),
                      speed_mean = round(mean(mean_speed), 2),
                      speed_sd = round(sd(mean_speed), 2),
                      speed_min = round(min(mean_speed), 2),
                      speed_max = round(max(mean_speed), 2),
                                 ) %>% 
            mutate("Nominal Temperature (°C) / Pressure (bar)" = paste(ntemp, npress, sep = " / "),
                   resp_mean = paste(resp_mean, resp_sd, sep =" \u00B1 "), 
                   resp_range = paste(resp_min, resp_max, sep = " - "),
                   temp_mean = paste(temp_mean, temp_sd, sep =" \u00B1 "), 
                   temp_range = paste(temp_min, temp_max, sep = " - "),
                   speed_mean = paste(speed_mean, speed_sd, sep =" \u00B1 "), 
                   speed_range = paste(speed_min, speed_max, sep = " - ")) %>%
            ungroup() %>% 
            select("Nominal Temperature (°C) / Pressure (bar)" , resp_mean, resp_range, temp_mean, temp_range, speed_mean, speed_range) %>%
            rename("Mean oxygen consupmtion rate (mg/kg/h)" = resp_mean,
                 "Range of oxygen consumption rates (mg/kg/h)" = resp_range,
                 "Mean observed temperature (°C)" = temp_mean,
                 "Range of observed temperatures (°C)" = temp_range,
                 "Mean observed velocity (BL/s)" = speed_mean,
                 "Range of velocities (BL/s)" = speed_range)
) %>% 
  autofit()
                     


```


**Tab 3** Short summary of the model statistics for main effects. Note, that value gives the change in the log of O2-consuption rate per change in one unit of the predictor.

```{r Tab 2}

intervals <- intervals(lme.plot)
intervals <- data.frame(intervals$fixed)
intervals <- intervals %>%
            rename(Lower_confidence_limit = lower,
                   Upper_confidence_limit = upper)
result <- as.data.frame(coef(summary(lme.plot)))
result$p <- result$'p-value'
result$Parameter <- rownames(result)
intervals$rownames <- rownames(intervals)


flextable(result %>%
  mutate(p = ifelse(p <= 0.001, "<0.001" , round(p, 3))) %>%
  left_join(intervals, by = c("Parameter" = "rownames")) %>%
  mutate("Lower conf. limit" = round(Lower_confidence_limit, 3),
         "Upper conf. limit" = round(Upper_confidence_limit, 3),
         Value = round(Value, 3)) %>%
  select(c('Parameter', 'Value', 'Lower conf. limit', 'Upper conf. limit', 'p')) %>% 
  mutate(Parameter = if_else(Parameter == "(Intercept)", "Intercept", 
                             if_else(Parameter == "temp_mean", "Temperature (°C)",
                             if_else(Parameter == "press_mean", "Pressure (bar)",
                             if_else(Parameter == "speedBL", "Velocity (BL/s)", "NA")))))) %>%
  autofit() 
 

```

\
\
\
\
\
\
\

## Graphs for the manuscript

```{r Fig 1, dpi = 300}

fig1a <- tag_facet2(
  ggplot(summary, aes(x=ID_time, y=log(resp))) +
  geom_point(aes(col = temp_mean, shape = as.factor(npress)), size=0.9, alpha = 0.5) +
  theme_bw()+
  scale_shape_manual(values = c(1, 16), guide = "none")+
  scale_colour_scico(palette = "batlow")+ # ,name = "temp (°C)" - this adds title for the specific legend
  geom_line(aes(x= ID_time, y=predict(lme.plot, level = 0)), size = 0.4)+
  geom_line(aes(x= ID_time, y=predict(lme.plot), group = ID), linetype = "dashed", size = 0.4)+
  labs(x = expression(time~(h)), y = expression(ln~O[2]-consumption ~(mg/kg %*% h^-1)))+
  facet_grid(run ~ tunnel, labeller = labeller(tunnel = tunnel.names, run = run.names))+
  guides(scale="none"), open ="", close ="", hjust = -1.2) +
  theme(legend.key.size = unit(3, "cm"),
      legend.key.width = unit(0.3, "cm"),
      legend.title = element_blank(),
      text = element_text(size = 10, family = "sans"))
  
  fig1b <- tag_facet2(
  ggplot(summary, aes(x=ID_time, y=log(resp_absol))) +
  geom_point(aes(col = temp_mean, shape = as.factor(npress)), size=0.9, alpha = 0.5) +
  theme_bw()+
  scale_shape_manual(values = c(1, 16), guide = "none")+
  scale_colour_scico(palette = "batlow")+ # ,name = "temp (°C)" - this adds title for the specific legend
  #geom_line(aes(x= ID_time, y=predict(lme.plot, level = 0)), size = 0.4)+
  #geom_line(aes(x= ID_time, y=predict(lme.plot), group = ID), linetype = "dashed", size = 0.4)+
  labs(x = expression(time~(h)), y = expression(ln~O[2]-consumption ~(mg %*% h^-1)))+
  facet_grid(run ~ tunnel, labeller = labeller(tunnel = tunnel.names, run = run.names))+
  guides(scale="none"), open ="", close ="", hjust = -1.2) +
  theme(legend.key.size = unit(3, "cm"),
      legend.key.width = unit(0.3, "cm"),
      legend.title = element_blank(),
      text = element_text(size = 10, family = "sans"))

#add plot with temp for qual check
  ggplot(summary, aes(x=datetime_min, y=temp_mean)) +
    theme_bw() +
    geom_point(aes(col = tunnel, shape = as.factor(npress)), alpha = 0.5)+
    scale_shape_manual(values = c(1, 16), guide = "none") +
    theme(legend.position = "none")
  

ggsave("Fig1a.pdf", fig1a, device = "pdf", height = 7, width = 8, dpi = 300)
ggsave("Fig1b.pdf", fig1b, device = "pdf", height = 7, width = 8, dpi = 300)

fig1a
fig1b
```

**Fig 1** Oxygen consumption rate per individual (a-i) over time different at temperatures (color scale) at 1 bar (open circles) and 8 bar (closed circles). Modeled predictions are displayed on the population level (solid line) and for the individual (dashed line). Colour indicates temp in °C\
\
\
\

```{r Fig 2, dpi = 300}


#ideal_summary <- ideal %>%
#  mutate(group = paste(temp_mean, press_mean, sep = "_")) %>% 
#  group_by(group) %>% 
#  summarize(mean = mean(resp),
#            sd = sd(resp))



fig2a <-  tag_facet2(ggplot(ideal_1, aes(x=temp_mean, y=resp)) +
  #geom_point(aes(colour = temp_mean)), size=1)+ 
  theme_bw()+
  stat_smooth(data = ideal_1, aes(x= temp_mean, y=resp, color = ID), se = F, size = 0.5, alpha = 0.75, geom="line", linetype = "solid")+
  stat_smooth(data = ideal_1, aes(x= temp_mean, y=resp_glob), se = F, size = 1, color = "black", alpha = 0.7, geom="line")+
  geom_point(data = summary, aes(x= temp_mean, y = resp, color = ID), alpha = 0.5)+
  #scale_colour_scico(palette = "batlow")+
  scale_colour_discrete(guide = "none")+
  #scale_linetype_manual(values=c(1,2), guide = "none") + 
  labs(linetype = "pressure (bar)", x = "temp (°C)", y = expression(O[2]-consumption ~(mg/kg %*% h^-1)))+
  facet_grid(run ~ tunnel, labeller = labeller(tunnel = tunnel.names, run = run.names))+
  theme(legend.position = c(.05, .95),
        legend.justification = c("left", "top"),
        legend.margin = margin(6, 6, 6, 6),
        legend.box.background = element_rect(color="black", size=1))+
  theme(text = element_text(size = 10, family = "sans")))


fig2b <-  tag_facet2(ggplot(ideal, aes(x=temp_mean, y=resp)) +
  theme_bw()+
  geom_point(data = summary, aes(x= temp_mean, y = resp, color = ID, shape = as.factor(npress)), alpha = 0.5)+
  scale_shape_manual(values = c(1, 16), guide = "none")+
  stat_smooth(data = ideal %>% filter(press_mean == 1), aes(x= temp_mean, y=exp(predict(lme.plot, newdata = ideal %>% filter(press_mean == 1))), color = ID), se = F, size = 0.4, geom="line", linetype = "solid")+
  stat_smooth(data = ideal %>% filter(press_mean == 8), aes(x= temp_mean, y=exp(predict(lme.plot, newdata = ideal %>% filter(press_mean == 8))), color = ID), se = F, size = 0.4, geom="line", linetype = "dashed")+
  stat_smooth(data = ideal %>% filter(press_mean == 1), aes(x= temp_mean, y=exp(predict(lme.plot, newdata = ideal %>% filter(press_mean == 1), level = "0"))), se = F, size = 0.4, color = "black", geom="line", linetype = "solid")+
  stat_smooth(data = ideal %>% filter(press_mean == 8), aes(x= temp_mean, y=exp(predict(lme.plot, newdata = ideal %>% filter(press_mean == 8), level = "0"))), se = F, size = 0.4, color = "black", geom="line", linetype = "dashed")+
  scale_colour_discrete(guide = "none")+
  labs(linetype = "pressure (bar)", x = "temp (°C)", y = expression(O[2]-consumption ~(mg/kg %*% h^-1)))+
  facet_grid(run ~ tunnel, labeller = labeller(tunnel = tunnel.names, run = run.names))+
  theme(legend.position = c(.05, .95),
        legend.justification = c("left", "top"),
        legend.margin = margin(6, 6, 6, 6),
        legend.box.background = element_rect(color="black", size=1))+
  theme(text = element_text(size = 10, family = "sans")))

fig2c <-  tag_facet2(ggplot(ideal, aes(x=temp_mean, y=resp)) +
  theme_bw()+
  geom_point(data = summary, aes(x= temp_mean, y = resp, color = speedBL, shape = as.factor(npress)), alpha = 0.5)+
  scale_shape_manual(values = c(1, 16), guide = "none")+
  scale_colour_scico(palette = "batlow")+
  stat_smooth(data = ideal %>% filter(press_mean == 1), aes(x= temp_mean, y=exp(predict(lme.plot, newdata = ideal %>% filter(press_mean == 1)))), se = F, size = 0.4, geom="line", linetype = "solid", color = "red")+
  stat_smooth(data = ideal %>% filter(press_mean == 8), aes(x= temp_mean, y=exp(predict(lme.plot, newdata = ideal %>% filter(press_mean == 8)))), se = F, size = 0.4, geom="line", linetype = "dashed", color = "red")+
  stat_smooth(data = ideal %>% filter(press_mean == 1), aes(x= temp_mean, y=exp(predict(lme.plot, newdata = ideal %>% filter(press_mean == 1), level = "0"))), se = F, size = 0.4, color = "black", geom="line", linetype = "solid")+
  stat_smooth(data = ideal %>% filter(press_mean == 8), aes(x= temp_mean, y=exp(predict(lme.plot, newdata = ideal %>% filter(press_mean == 8), level = "0"))), se = F, size = 0.4, color = "black", geom="line", linetype = "dashed")+
  #scale_linetype_manual(values=c(1,2), guide = "none") + 
  labs(linetype = "pressure (bar)", x = "temp (°C)", y = expression(O[2]-consumption ~(mg/kg %*% h^-1)))+
  facet_grid(run ~ tunnel, labeller = labeller(tunnel = tunnel.names, run = run.names))+
  theme(legend.key.size = unit(3, "cm"),
      legend.key.width = unit(0.3, "cm"),
      legend.title = element_blank(),
      text = element_text(size = 10, family = "sans")))

fig2d <-  ggplot(ideal_1, aes(x=temp_mean, y=resp)) +
  #geom_point(aes(colour = temp_mean)), size=1)+ 
  theme_bw()+
  stat_smooth(data = ideal_1, aes(x= temp_mean, y=resp, group = ID, color = startmass), se = F, size = 0.5, alpha = 0.75, geom="line", linetype = "dashed")+
  stat_smooth(data = ideal_1, aes(x= temp_mean, y=resp_glob), se = F, size = 1, color = "black", alpha = 0.7, geom="line")+
  scale_colour_scico(palette = "batlow")+
  #scale_colour_discrete(guide = "none")+
  #scale_linetype_manual(values=c(1,2), guide = "none") + 
  labs(linetype = "pressure (bar)", x = "temp (°C)", y = expression(O[2]-consumption ~(mg/kg %*% h^-1)))+
  theme(legend.position = c(.05, .95),
        legend.justification = c("left", "top"),
        legend.margin = margin(6, 6, 6, 6),
        legend.box.background = element_rect(color="black", size=1))+
  theme(text = element_text(size = 10, family = "sans"))

ggsave("Fig2a.pdf", fig2a, device = "pdf", height = 7, width = 8, dpi = 300)
ggsave("Fig2b.pdf", fig2b, device = "pdf", height = 7, width = 8, dpi = 300)
ggsave("Fig2c.pdf", fig2c, device = "pdf", height = 7, width = 8, dpi = 300)
ggsave("Fig2d.pdf", fig2d, device = "pdf", height = 7, width = 8, dpi = 300)

fig2a
fig2b
fig2c
fig2d

```

**Fig 2** Predicted oxygen consumption rate at different temperatures and pressures at a swimming speed of 0.6 BL/s.  Difference between 1 and 8 bar is not significant.\
\
\
\
\
\
\

## Graphs/tabs for supplementary

**Tab S1** Summary of experimental parameters and oxygen consumption grouped by individual, nominal temperature and pressure. Note, that temperature means and ranges are calculated from the mean temperature of individual measurements (since for each measurement only a single oxygen consumption rate is available). 

```{r}

calc_n <- summary %>% mutate(indicator = paste(ID, ntemp, npress, sep = "_")) %>% 
                      group_by(indicator) %>% 
                      summarize(n = length(estimate_s))

addresp <- summ_by_ID %>% 
  ungroup() %>% 
  mutate(indicator = paste(ID, ntemp, npress, sep = "_")) %>% 
  select(-ntemp, -npress, -ID) %>%
  mutate_at(1:8, round, 1) %>%
  mutate_at(8:12, round, 2) %>%
  mutate(t = paste(mean_temp, sd_temp, sep = " \u00B1 "),
         t_range = paste(min_temp, max_temp, sep = " - "),
         o = paste(mean_temp, sd_temp, sep = " \u00B1 "),
         o_range = paste(min_temp, max_temp, sep = " - "),
         s = paste(mean_speed, sd_speed, sep = " \u00B1 "),
         s_range = paste(min_speed, max_speed, sep = " - ")) %>% 
  select(indicator, t, t_range, o, o_range, s, s_range) %>% 
  rename("Mean observed temperature (°C)" = t,
         "Observed Temperature range (°C)" = t_range,
         "Mean oxygen consumption (mg/kg/h)" = o,
         "Oxygen consumption range (mg/kg/h)" = o_range,
         "Mean observed velocity (BL/s)" = s,
         "Observed velocity range (BL/s)" = s_range)
         
flextable(biomasses %>%
            select(ID, ID_old) %>% 
            left_join(treattime, by = c("ID_old" = "ID")) %>%
            mutate(ntemp = replace(ntemp, ntemp == "15", 15.5),
                   indicator = paste(ID_old, ntemp, npress, sep = "_")) %>%
            left_join(calc_n, by = "indicator") %>%
            left_join(addresp, by = "indicator") %>% 
            select(-start, -end, -time_h, -indicator, -ID_old) %>%
            mutate(time_d = round(time_d, 1)) %>%
            rename("nominal pressure (bar)" = npress,
                   "nominal temperature (°C)" = ntemp,
                   "swim time (d)" = time_d)) %>% 
          colformat_num(big.mark   = "") %>%
  autofit()

```

**Tab S2** Summary of model AICs

```{r Tab S1}

round_df <- function(x, digits) {
    # round all numeric variables
    # x: data frame 
    # digits: number of digits to round
    numeric_columns <- sapply(x, mode) == 'numeric'
    x[numeric_columns] <-  round(x[numeric_columns], digits)
    x
}

remotes::install_github("davidgohel/flextable")
library(flextable)

AIC_scores <- select.lme %>%
         mutate_if(is.numeric, round, 2) %>% 
         replace(is.na(.), "") %>% 
         slice(1:5)
                
AIC_scores <- flextable(AIC_scores) 

FitFlextableToPage <- function(ft, pgwidth = 6){

  ft_out <- ft %>% autofit()

  ft_out <- width(ft_out, width = dim(ft_out)$widths*pgwidth /(flextable_dim(ft_out)$widths))
  return(ft_out)
}

FitFlextableToPage(AIC_scores)
 
```

\
\
\
\

```{r Fig S1, dpi = 600}

ggplot(summary, aes(x=speedBL, y=resp)) +
    geom_point(size=0.2)+ 
    theme_bw()+
    theme(text = element_text(size = 8, family = "sans")) +
    xlim(0.4, 0.8)+
    facet_nested(ntemp + npress ~ Letter_ID )+
  labs(linetype = "pressure (bar)", x = "flow rate (body length/s)", y = expression(O[2]-consumption ~(mg/kg %*% h^-1)))+
  theme(axis.text.x = element_text(angle = 45, size = 6))+
  theme(axis.text.y = element_text(size = 8))+
  geom_smooth(method='lm', formula= y~x, se = F, size = 0.7)
```

**Fig S1** Effect of swimming speed on Oxygen consumption rate per Temperature and pressure for each individual
